### 2021-10-23 aifin/2021/project2/project2.tex

The requirements of this paper replication project are as follow:
\begin{itemize}
\item The machine learning methods used in this paper include linear regression (OLS, elastic net), dimension reduction (PLS, PCR), generalized linear models, trees (gradient boosting trees, random forest) and neural networks. Please try to replicate \textbf{at least 6 methods} of them (e.g., OLS, elastic net, PLS, PCR, random forest, neural networks, etc. Please note that if you choose OLS, OLS-3 should also be included; and if you choose neural network, NN1 to NN5 are included. Besides, robust loss function should also be considered. See details in the paper), and analyze your results specifically. Hints on parameter choice are presented in the paper.
\item Include the variable importance (section 2.3 of the paper) in your analysis. You do not need to replicate all the figures in section 2.3, but you are encouraged to investigate it carefully.
\item Note that this paper uses a `recursive performance evaluation scheme'. You are also required to evaluate your result by this method. For more details of this method, please refer to the paper and its supplementary material. The PPT presented in class about this project may also be helpful to you.
\item As you can know from the paper, the 8 macroeconomic predictors are constructed following Welch and Goyal (2008), and it is not directly included in the dataset. You should construct them by yourself.
\item The portfolio forecast part of the paper (section 2.4) is not compulsory for you to replicate.
\end{itemize}

>>>>

The requirements of this paper replication project are as follow:
\begin{itemize}
\item The machine learning methods used in this paper include linear regression (OLS, elastic net), dimension reduction (PLS, PCR), generalized linear models, trees (gradient boosting trees, random forest) and neural networks. Please try to replicate \textbf{at least 6 methods} of them (e.g., OLS, elastic net, PLS, PCR, random forest, neural networks, etc. Please note that if you choose OLS, OLS-3 should also be included; and if you choose neural network, NN1 to NN5 are included. Besides, robust loss function should also be considered. See details in the paper), and analyze your results specifically. Hints on parameter choice are presented in the paper.
\item Include the variable importance (section 2.3 of the paper) in your analysis. You do not need to replicate all the figures in section 2.3, but you are encouraged to investigate it carefully.
\item Note that this paper uses a `recursive performance evaluation scheme'. You are also required to evaluate your result by this method. For more details of this method, please refer to the paper and its supplementary material. The PPT presented in class about this project may also be helpful to you.
\item As you can know from the paper (section 2.1), predictive characteristics include firm characteristics, sic code and macroeconomic predictors. Firm characteristics and sic code are provided in the original dataset of this paper, and the 8 macroeconomic predictors are constructed following Welch and Goyal (2008), which are not directly provided in the original dataset of this paper. Hence, you may construct the predictors by yourself according to the description in Welch and Goyal (2008), for instance, see \\
\url{https://christophj.github.io/replicating/r/replicating-goyal-welch-2008/}.
\item The portfolio forecast part of the paper (section 2.4) is not compulsory for you to replicate.
\end{itemize}
